---
title: "Clustering homework"
author: "A Hameed"
date: "24/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

 
```{r}
library(tidyverse)
library(janitor)
```
 
# loading customers data and cleanning names
```{r}
customers <- read_csv("data/mall_customers.csv") %>% 
  clean_names()

customers
```
 
# check if any na
```{r}
any(is.na(customers))
```
 
 
# Select only numerical column
```{r}
customers <- customers %>% 
  select(-customer_id, -gender)  
  #column_to_rownames("gender")
customers
```
 
# Scaling data 
```{r}
customers_scaled <- customers %>% 
  mutate_all(scale)
customers_scaled
```
 
# checking the relations between spending score and annual income 
It is look like a meaningful and we could make cluster as there is a gap between data.
```{r}
customers_scaled %>% 
ggplot( aes(y = annual_income_k, x = spending_score_1_100)) +
  geom_point()
```
 
 # Perform k-means clustering and chose a value of k.
 
we will use the 3 different method to check how many K should we use in customer data.
```{r}
library(factoextra)
 fviz_nbclust(customers_scaled, 
             kmeans, 
             method = "wss", 
             nstart = 25)
```
 
 
```{r}
fviz_nbclust(customers_scaled, 
             kmeans, 
             method = "silhouette", 
             nstart = 25)
```
 
 
 
```{r}
fviz_nbclust(customers_scaled, 
             kmeans, 
             method = "gap_stat", 
             nstart = 25, 
             k.max = 10)
```
 
 The 3 different method confirm that the K should be 6. 
 
 
 
# Visualise the clustering k = 6.
```{r}
library(broom)

 max_k <- 6 

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(customers_scaled, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, customers)
  )

k_clusters
```
 
```{r}
k_clusters %>% 
  unnest(cols = c(augmented)) %>%
  ggplot() +
  aes(y = spending_score_1_100,
      x = annual_income_k,
      color = .cluster) +
  geom_point(aes(color = .cluster))
```
 
 # Do you think the clustering seems a good fit for this data?
 
No as the blue and red clusters are mixed together I think the not good fit might k =4 or less will be a good fit.
below I tried to test the K manually 3,4 and 5. I can't find the good one to fit the data.

```{r}
k_clusters %>% 
  unnest(cols = c(augmented)) %>%
  filter(k <= 3) %>%
  ggplot() +
  aes(y = spending_score_1_100,
      x = annual_income_k,
      color = .cluster) +
  geom_point(aes(color = .cluster))
```

