---
title: "Hypothesis tests & probability - homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

<hr>

# MVP

## Hypothesis testing - practical

You work for an animal conservation organisation and are looking to do some investigating into some of the animals to provide evidence for some projects you are looking to run. 

In this homework we'll use the `msleep` data set provided in the `ggplot` package. It concerns the sleeping patterns of various types of mammal.

```{r, message = FALSE, warning=FALSE}
library(tidyverse)
data(msleep)
library(infer)
```

<br>

**Question 1.**  
Explore the dataset and familiarise yourself with it.
```{r}
msleep %>% 
  glimpse()
```

<br>

**Question 2.**  
Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean `sleep_total` in the sampled population of animal types differs from the typical value for jabberwockies.
 
<br>
 
We wanted to investigate whether the average (sleep_total) is significantly different from a given Jabberwockies sleep for around 7 hours.

alpha is 0.05 
H0: μ sleep_total= 7 (the population sleep_total is 7)
Ha: μ sleep_total =/= 7 (the population mean is different from 7)

```{r}
msleep <- msleep %>% 
  filter(!is.na(sleep_total))

msleep %>%
  ggplot(aes(x = sleep_total)) +
  geom_histogram(col = "white", bins = 30)
```


```{r}
observed_stat <- msleep %>%
   summarise(mean_sleep_total = mean(sleep_total))

observed_stat
```
# Calculate the null sampling distribution
```{r}
null_distribution <- msleep %>%
  specify(response = sleep_total) %>%
  hypothesize(null = "point", mu = 7) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")
null_distribution
```

# we use both in direction as we  are interested in differences from 7
```{r}
null_distribution %>%
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat$mean_sleep_total, direction = "both")
```
The observed statistic (x¯) 10.43373 is marked with a red line in the histogram


```{r}
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat$mean_sleep_total, direction = "both")
p_value
```

#sumaray: the p value is less than our alpha 0.05 so  we will reject H0 in favour of Ha as thee current mean(sleep_total) of 10.43373 is significantly different to the value Jabberwockies sleep for around 7 hours


**Question 3.**  
Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

<br>
so we have two vores of animals and we are interested in hypotheses about the difference in  means μ1−μ2.lets set our conventional significance level α=0.05 and write our hypotheses.

H0 : μ sleep(omnivores)− μ sleep(herbivores) = 0
Ha: μ sleep(omnivores)− μ sleep(herbivores) > 0


```{r}
msleep_tidy <- msleep %>% 
  filter(vore == "omni" |  vore == "herbi") %>% 
  select(vore, sleep_total)
msleep_tidy
```

```{r}
msleep_tidy %>% 
  ggplot(aes(x = vore, y = sleep_total)) +
  geom_boxplot() +
  labs(
    x = "\nvore",
    y = "sleep total",
    title = "animals"
  )
```

```{r}
null_distribution <- msleep_tidy %>% 
    specify(sleep_total ~ vore) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>% 
calculate(stat = "diff in means", order = c("omni", "herbi")) # our stat is the mean of omni minus mean of herbi
 head(null_distribution)
```


# visualise the null distribution
```{r}
null_distribution %>% 
  visualise(bins = 30)
```
 
we need to calculate our observed statistic as we have the null distribution, then we visualise the null distribution and where the observed statistic lies on the distribution.

```{r}
observed_stat <- msleep_tidy %>% 
    specify(sleep_total ~ vore) %>%
  calculate(stat = "diff in means", order = c("omni", "herbi"))
   
observed_stat
```

```{r}
null_distribution %>% 
  visualise() +
    shade_p_value(obs_stat = observed_stat, direction = "right")
```

 Let’s calculate the p-value.
```{r}
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "right")

p_value
```

# Conclusion 
 The P valu 0.152 is greater than our alpha 0.05 therefore fail to reject H0 and confirm that we have not found enough evidence in our data to suggest that the average omnivores sleep for significantly longer than herbivores.
 
 
**Question 4. **
Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than $5\%$.
<br>
<details>
<summary>**Hint**</summary>
Think about creating an `is_domesticated` variable for the analysis
</details>

# First lets creating an `is_domesticated` column
```{r}
msleep_tidy_prop <- msleep %>%
  mutate(is_domesticated = ifelse(conservation == "domesticated", "domesticated", "not_domesticated"))


head(msleep_tidy_prop)
```

# calculate the proportion of domesticated 
```{r}
msleep_tidy_prop %>%
  group_by(is_domesticated) %>%
  summarise(prop = n()/nrow(msleep_tidy_prop)) %>%
  filter(is_domesticated == "domesticated")
```

#In the population the proportion of domesticated  is 12%. This is  greater than 5%, but we want to know if this difference from 5% is statistically significant or not



Let’s start by setting a significance level α=0.05, and setting up our hypotheses:


H0: πdomesticated =0 .05
Ha: πdomesticated >0.05
<hr>

```{r}
null_distribution <- msleep_tidy_prop %>%
  specify(response = is_domesticated, success = "domesticated") %>% 
  hypothesize(null = "point", p = 0.05) %>%
  generate(reps = 5000, type = "simulate") %>%
  calculate(stat = "prop")  

head(null_distribution)
```

Let’s visualise this distribution

```{r}
null_distribution %>%
  visualise(bins = 30)
```

# we calculate the observed stat which is 18.5%

```{r}
observed_stat <-  msleep_tidy_prop %>%
  specify(response = is_domesticated, success = "domesticated") %>% 
  calculate(stat = "prop")  

observed_stat
```
```{r}
null_distribution %>%
  visualise(bins = 30) +  
  shade_p_value(obs_stat = observed_stat, direction = "both")  
```
# Our observed statistic is quite far to the right hand side of the null distribution. 

lets caculate the p value 
```{r}
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "both")

p_value
```

 The p-value is less than our significance level 0.05. So we will reject H0 in favour of Ha. Based on the data, proportion of domesticated animal types in the population of animal types is greater than 5%
 
 

## Hypothesis testing - Defining the Hypothesis 

For the following three business problems write out:

* What kind of test you would use  
*  $H_0$ and $H_a$ in **both** mathematical notation and in words. 
* Also state the method you would use to generate the null distribution (bootstrap, permutation or simulation). 

<br>

**Question 1.**  
You work for a independent coffee shop. The boss tells you that she thinks that around $40\%$ of people in the town (population $30,000$) know of the coffee shop, but you are skeptical of the estimate. You conduct a random survey of $200$ people in the town, asking if respondents are aware of your coffee shop. You want to use the sample to test the hypothesis that $40\%$ or more of the town's population have heard of the coffee shop. 

<br>
# we will use One-sample mean test we will comparing the mean from one sample against our value 40%
# H0: know the coffee shop < 40%
  Ha: know the coffee shop >= 40%
# The method we use here to generation of null distibution is a boostrap with replacement from our original sample (200)
  
  
  
**Question 2.**  
You work for a website design company and have performed an **A/B test** on the position of a banner on a website promoting a particular item. 
<br><br>
<div class='emphasis'>
**A/B testing** 
A method comparing two versions of a web page, email, flyer or other marketing device against each other to determine which version performs better. As it is essentially a controlled experiment, the design should try to ensure that the groups experiencing both versions of the marketing device are equivalent and representative of the population.
</div>
<br><br>
You selected five days at random last month and then randomly selected $200$ of each sampled day's users into group $A$ and another $200$ of that day's users into group $B$. Group $A$ continued to be shown the banner at the right hand side of the webpage (its usual position) while group $B$ was shown the banner at the top of the page. You monitored each sampled user's interactions with the website, in particular the 'click through rate' (CTR) on the banner, i.e. what proportion of sampled users clicked on the banner. You want to use the sampled data to test the hypothesis that website users overall are more likely to click on the banner if positioned at the top of the page   
<br>

# we will use two samples test independent samples
Null hypothesis H0: μ1−μ2=0
Statistic: x¯A−x¯B=1.50
the method we would use to generate the null distribution is permutation.

**Question 3.**  
You work as an analyst for a car manufacturing company - they have specific standards they must meet for standards and regulation purposes. You have been asked to check the quality control of the manufacture of a particular car part. You have been given data on a sample of $200$ parts produced over the period of a week (the sampled parts were pulled at random from the production line and measured: the factory produced a lot more than $200$ parts that week). The specification of the part stipulates a width of $145\textrm{mm}$, and the manufacturing process is said to have 'drifted' if the mean width of parts differs significantly from $145\textrm{mm}$. You want to use the sampled measurements to test whether the process overall has drifted.     

#  we will use One-sample proportion test
Null hypothesis H0: π0=145
Ha: M drifted̂ =/=145mm
the method we would use to generate the null distribution is simulate.



## Hypothesis Testing - Interpreting the results

For the 3 business problems stated above, imagine we performed you got the following p-values (with the given significance levels) write out your interpretation of the results. 

<br>

**Question 1.**  

**Coffee shop problem**. Significance level: 0.05, calculated $p$-value: 0.07
# we will reject H0 and confirm that 40% or more of the town's population have heard of the coffee shop.

<br>

**Question 2.**  

**Website company problem**. Significance level: 0.01, $p$-value: 0.006
# P value is less than our significance level so both versions of the marketing device are equivalent and representative of the population. and we will reject H0.

<br>

**Question 3.**  

**Manufacturing company problem**. Significance level: 0.05, $p$-value: 0.55

# as the p-value is greater than alpha 0.05 so we fail to reject null hypotisis H0 therefore,
  we do not have enough evident that the mean width of parts differs is significantly from 145mm. 


