---
title: "Simple linear regression homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
  pdf_document: default
---
 
<!--   body{ -->
<!--   font-size: 8pt; -->
<!-- } -->
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(janitor)
library(ggfortify)
library(broom)
library(infer)
```


# Load the data.
<details>
<summary>**Answer**</summary>

```{r}
project <- read_csv("data/project_management.csv")
project
```

</details>

# Plot the data.

<details>
<summary>**Answer**</summary>
 The graph shows when we increase x, y also increases.
```{r}
project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() 
```


 
 </details>

# Calculate the correlation.
<details>
<summary>**Answer**</summary>
From the positive  results of the correlation we would say that these variables are very strongly positively linearly correlated. 
```{r}
project %>% 
  summarise( correlation = cor(estimated_length, actual_length))
```

</details>

# Perform a simple linear regression.  
<details>
<summary>**Answer**</summary>

```{r}
model <- lm(formula = actual_length ~ estimated_length, data = project)
model
```


</details>

# Interpret the regression coefficient and the r2 value reported by the model.

<details>
<summary>**Answer**</summary>


```{r}
tidy_output <- model %>% 
  tidy() %>% 
  clean_names()

tidy_output 
```

```{r}
glance_output <- model %>% 
  glance() %>% 
  clean_names()
glance_output
```

 The r squared shows that our simple linear model says that 64.7% of the variation in actual_length in the sample data can be explained by variation in estimated_length

</details>

# Is the relationship statistically significant? 
<details>
<summary>**Answer**</summary>

```{r}
autoplot(model)
```

The  bootstrap below is for extract the slope, coefficient and confidence level 95%.
```{r}
bootstrap_distribution_slope <- project %>%
  specify(formula = estimated_length ~ actual_length) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "slope")

slope_ci95 <- bootstrap_distribution_slope %>%
  get_ci(level = 0.95, type = "percentile")
slope_ci95
```
```{r}
bootstrap_distribution_slope %>%
  visualise(bins = 30) +
  shade_ci(endpoints = slope_ci95)
```


```{r}
clean_names(tidy(model, conf.int = TRUE, conf.level = 0.95))
```

</details>




