---
title: "prob Homework"
output:
  html_document:
    df_print: paged
---

```{r, message = FALSE}
library(prob)
library(gtools)
library(tidyverse)
```
 #1 MVP
#1.1 The Titanic
# Reading the data
```{r}
titanic_data <- read_csv("data/titanic.csv")
titanic_data
```

```{r}
titanic_data %>% 
  distinct(class)
```

# Create a new column crew hold True if crew or staff and false if not
```{r}
titanic_data <- titanic_data %>% 
  mutate(crew = ifelse(str_detect(class, "crew") |  str_detect(class, "staff"), TRUE, FALSE))

titanic_data  
```

# The probability of being crew and survived
```{r}
prob_crew_servied <- titanic_data %>%
  filter(survived == "yes", crew == TRUE) %>%
  summarise(prob = n() / nrow(titanic_data))
prob_crew_servied
```
# The probability of being survived and not crew (passenger) 
```{r}
prob_passenger_servied <- titanic_data %>%
  filter(survived == "yes", crew == FALSE) %>%
  summarise(prob = n() / nrow(titanic_data))
prob_passenger_servied
```
# so the prob(crew)

```{r}
prob_crew <- titanic_data %>% 
  filter(crew == TRUE) %>% 
summarise(prob_crew = n() / nrow(titanic_data))
prob_crew
```

# so the prob(passenger)

```{r}
prob_passenger <- titanic_data %>% 
  filter(crew == FALSE) %>% 
summarise(prob_passenger = n() / nrow(titanic_data))
prob_passenger
```

# so prob(survived∣crew) = prob(survived ∩ crew) /prob(crew)
```{r}
prob_servied_given_crew <- prob_crew_servied / prob_crew
prob_servied_given_crew
```
# so prob(survived∣passenger) = prob(survived ∩ passenger) /prob(passenger)
```{r}
prob_servied_given_passenger <- prob_passenger_servied / prob_passenger
prob_servied_given_passenger
```

# 1.2 Probability Consolidation Questions
# Q1 If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
s_one_dice <- rolldie(1)

s_one_dice %>% 
  filter(X1 <= 5) %>% 
  summarise(less_than_5 = n() / nrow(s_one_dice))
```

