---
title: "R Notebook"
output: html_notebook
---




# Question 1. 

Load in the libraries you need, and look at the `backpack` data. Take note of variable names and dimensions.   
```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
backpack %>% 
  glimpse()
```


# Question 2

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

From the graph below the majority of student carrying around 10 only few student carrying >30 or < 5
```{r}
backpack %>% 
  ggplot(aes(x = backpack_weight)) +
  geom_bar() +
  labs( title = "No of students carrying backpack weights",
       x = "\n Wackpack Weights",
       y = "No of students currying Weights")
```
# Question 3.

Are there differences in backpack weight between sex?
```{r}
backpack %>% 
  ggplot(
        aes(x = backpack_weight, y = sex,  color = sex)) +
  geom_line() 
```


# Question 4.

What is the relationship between body weight and backpack weight?

```{r}
backpack %>% 
ggplot(aes(x = body_weight, y = backpack_weight)) + 
    geom_point()
```


# Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
backpack %>% 
ggplot(aes(x = body_weight, y = backpack_weight)) + 
    geom_point() +
  facet_wrap(~ sex)
```


# Question 6.

What proportion of students report back pain?

```{r}
backpack %>% 
ggplot(aes(x = back_problems)) + 
    geom_bar()
```


